Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-10 edubots_surveys.Rnw
Updating biblio
small edit previously approved but not commited

We collected responses from 282 teachers from Spain and Spanish-speaking
countries for \textit{survey1} and 205 for \textit{survey2}. The two forms were
open for approximately the same amount of time, around two months. Most responders were university teachers, although about 32\% of them in \textit{survey1} and 8\% (in \textit{survey2} are from
non-universitary tertiary education teachers. With respect to
gender, 61\% of teachers were male and 32\% female, while approximately 5\%
chose not to disclose their gender. Finally, the responses are more or less equally
distributed according to the teacher's years of experience, showing 24\% of responses from
teachers with 5 or less years of experience, 26\% for 6-15 years of experience,
30\% for 16-25, and 20\% for teachers with more than 25 years of experience.

>>>>

% Describe the survey and population
We collected responses from 282 teachers from Spain and Spanish-speaking
countries for \textit{survey1} and 205 for \textit{survey2}. The two forms were
open for approximately the same amount of time, around two months. The sample
includes mostly university teachers, although about 32\% and 8\% are from
non-universitary tertiary education in the first and second survey respectively. Regarding
gender, 61\% of teachers were male and 32\% female, while approximately 5\%
chose not to disclose it. Finally, the responses are more or less equally
distributed according to the teaching experience, showing 24\% of responses from
teachers with 5 or less years of experience, 26\% for 6-15 years of experience,
30\% for 16-25, and 20\% for teachers with more than 25 years of experience.
